Supporting Information:\\ Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-08-20 Manuscript/manuscriptPSsuppl.tex
change in the numbering of pages of SI completed method section in SI covering CHARMM36 NBFIX2 simulations

@@

\noindent
{\it POPC:POPS (5:1) mixtures with additional calcium using NBfix1 parameters.} 
POPC:POPS (5:1) mixtures containing total 300 (250:50) lipids
%were simulated with the additional calcium concentrations.
%The data is available from Refs. \citenum{POPC5POPS1withCaClCHARMM} and \citenum{POPC5POPS1with1MCaClCHARMM}.
and 0.26~M and 1~M CaCl$_2$ were prepared using the CHARMM-GUI in Janyary 2018 \cite{lee16,jo18}.
The ion parameters generated by CHARMM-GUI at the time are labeled here as NBfix1~\cite{kim16}.
Systems were simulated using Gromacs 5 \cite{abraham2015gromacs} and CHARMM36 force field with the simulation parameters given
by the CHARMM-GUI at 298~K. \\

\noindent
{\it POPC:POPS (5:1) mixtures with additional calcium using NBfix1 parameters.}
\todo{Ricky, please update the simulation methods.}
Systems were prepared using the CHARMM-GUI in August 2019 \cite{lee16,jo18}.
The ion parameters generated by CHARMM-GUI at the time are labeled here as NBfix2~\cite{han2018graph}.

>>>>

\setcounter{page}{0}

@@

\noindent
{\it POPC:POPS (5:1) mixtures with additional calcium using NBfix1 parameters.} 
POPC:POPS (5:1) mixtures containing total 300 (250:50) lipids
%were simulated with the additional calcium concentrations.
%The data is available from Refs. \citenum{POPC5POPS1withCaClCHARMM} and \citenum{POPC5POPS1with1MCaClCHARMM}.
and 0.26~M and 1~M CaCl$_2$ were prepared using the CHARMM-GUI in January 2018 \cite{lee16,jo18}.
The ion parameters generated by CHARMM-GUI at the time are labeled here as NBfix1~\cite{kim16}.
Systems were simulated using Gromacs 5 \cite{abraham2015gromacs} and CHARMM36 force field with the simulation parameters given
by the CHARMM-GUI at 298~K. \\

\noindent
{\it POPC:POPS (5:1) mixtures with  additional calcium using NBfix2 parameters.}
POPC:POPS (5:1) mixtures containing total 300 (250:50) lipids, neutralizing sodium ions, 
and 0.14~M or 0.94~M CaCl$_2$ were prepared using the CHARMM-GUI in August 2019 \cite{lee16,jo18}.
The ion parameters generated by CHARMM-GUI at the time are labeled here as NBfix2~\cite{han2018graph}. Systems were simulated using Gromacs 2018.6 \cite{abraham2015gromacs} and CHARMM36 force field with the simulation parameters given
by the CHARMM-GUI at 320~K.  \\
